---
title: "C3.ai data sampling notebook (Multi-variate Methods)"
output: html_notebook
---

# C3.ai COVID-19 Data Lake - Data Sampling (Multi-variate Methods)

This notebooks collects all available data for the Quantum-like Bayesian network interface.

For the time being, we are using a simplified model in which only the data segment but not the header segment will be created for event types.

To view an outline of this notebook, use the RStudio keyboard shortcut Control + Shift + O on Windows or Command + Shift + O on Mac.

Remark: Some of the packages may not be needed, use the following (sample) code to load packages instead:

#define a function to install and load required packages
ipak <- function(pkg){
  new.pkg <- pkg[!(pkg %in% installed.packages()[, "Package"])]
  if (length(new.pkg)) 
    install.packages(new.pkg, dependencies = TRUE)
  sapply(pkg, require, character.only = TRUE)
}

#specify a list of required packages
pack_list <- c("dplyr",
               "lubridate",
               "NCmisc")

#install and load packages
suppressWarnings(ipak(pack_list))

#define current working directory
current_wd <- dirname(rstudioapi::getActiveDocumentContext()$path)
setwd(current_wd)

#cross-check unused packages
used_packages <- list.functions.in.file(rstudioapi::getSourceEditorContext()$path) %>%
  names() %>%
  unique()
pack_list <- paste0("package:",unlist(pack_list))
print("Unused packages:")
print(setdiff(pack_list,used_packages))
print("Missing packages:")
print(setdiff(used_packages,pack_list))

```{r}
if (!require(plyr)) install.packages('plyr')
if (!require(dplyr)) install.packages('dplyr')
if (!require(pbmcapply)) install.packages('pbmcapply')
if (!require(stats)) install.packages('stats')
if (!require(lubridate)) install.packages('lubridate')
if (!require(fuzzyjoin)) install.packages('fuzzyjoin')
if (!require(gtools)) install.packages('gtools')
if (!require(tidyr)) install.packages('tidyr')
if (!require(stringr)) install.packages('stringr')
if (!require(uuid)) install.packages('uuid')
if (!require(data.table)) install.packages('data.table')
if (!require(rlist)) install.packages('rlist')
if (!require(ggplot2)) install.packages('ggplot2')

library(plyr)
library(dplyr)
library(pbmcapply)
library(stats)
library(lubridate)
library(fuzzyjoin)
library(gtools)
library(tidyr)
library(stringr)
library(uuid)
library(data.table)
library(rlist)
library(ggplot2)
```

Define maximum data validity

```{r}
seconds_back <- 6*60*60-1
seconds_ahead <- 6*60*60-1
```


Function to collect all data

```{r}
start_time <- as.character(Sys.time())

#get existing scope for sampling
object_types <- read.csv(file="../events/objectTypeIDs.csv",
                         header=TRUE,
                         sep=";")
measures <- read.csv(file="../events/measureIDs.csv",
                         header=TRUE,
                         sep=";") %>%
              mutate(.,
                     uuidMeasure=uuidMeasure,
                     description=paste0(source,
                                        "_",
                                        description,
                                        "_",
                                        scaleLevel),
                     number=seq(1,nrow(.)),
                     .keep="none")
objects <- read.csv(file="../events/objectIDs.csv",
                         header=TRUE,
                         sep=";") %>%
             select(.,
                    -iso) %>%
             left_join(.,
                       object_types,
                       by="uuidObjectType") %>%
             mutate(.,
                    description=paste0(description.y,
                                       "_",
                                       description.x),
                    number=seq(1,nrow(.)),
                    .keep="unused")
valid_records <- expand.grid(measures$number,
                             objects$number) %>%
                   left_join(.,
                             measures,
                             by=c("Var1"="number")) %>%
                   left_join(.,
                             objects,
                             by=c("Var2"="number")) %>%
                   select(.,
                          -c(Var1,
                             Var2)) %>%
                   mutate(.,
                          eventType=paste0(uuidObjectType,
                                           "_",
                                           uuidMeasure))

#cross-check list against existing files
existing_files <- list.files(path="../events/") %>%
                    substr(.,
                           1,
                           nchar(.)-4)
valid_records <- valid_records[which(valid_records$eventType %in% existing_files),]
valid_records$number <- seq(1,
                            nrow(valid_records))
files <- unique(valid_records$eventType)

#get existing validity periods
timestamps <- pbmclapply(files,FUN=function(x) {
                           load(paste0("../events/",
                                       x,
                                       ".rda"))
                           data <- mutate(data,
                                          measurementTime=with_tz(data$measurementTime,
                                                                  tzone="UTC"))
                           return(as.character(data$measurementTime))
              },mc.cores=8L) %>%
                unlist() %>%
                unique()
timestamps <- interval(timestamps,
                       timestamps)
int_start(timestamps) <- int_start(timestamps) - seconds_back
int_end(timestamps) <- int_end(timestamps) + seconds_ahead
timestamps <- data.frame(validity=timestamps,
                         number=seq(1,
                                    length(timestamps)))

#re-calculate valid records
valid_records <- expand.grid(valid_records$number,
                             timestamps$number) %>%
                   left_join(.,
                             valid_records,
                             by=c("Var1"="number")) %>%
                   left_join(.,
                             timestamps,
                             by=c("Var2"="number")) %>%
                   select(.,
                          -c(Var1,
                             Var2)) %>%
                   select(.,
                          eventType,
                          uuidMeasure,
                          uuidObject,
                          validity) %>%
                   dlply(.,
                         "eventType")

#load required event records
event_records <- pbmclapply(1:length(valid_records),FUN=function(x) {
                   load(paste0("../events/",
                               names(valid_records[x]),
                               ".rda"))
                   data <- mutate(data,
                                  measurementTime=with_tz(data$measurementTime,
                                                          tzone="UTC")) %>%
                             left_join(valid_records[[x]],
                                       data,
                                       by="uuidObject") %>%
                             .[which(.$measurementTime %within% .$validity),] %>%
                             select(.,
                                    uuidMeasure,
                                    uuidObject,
                                    validity,
                                    measurementValue) %>%
                             mutate(.,
                                    validity=as.character(validity))
                   return(data)
                 },mc.cores=8L)

end_time <- as.character(Sys.time())

names(event_records) <- names(valid_records)
event_records <- event_records %>%
                   ldply(.parallel=TRUE,
                         .id="eventType") %>%
                   mutate(.,
                          uuidObjectType=substr(eventType,
                                            1,
                                            36),
                          measurementValue=as.numeric(measurementValue),
                          .keep="unused") %>%
                   left_join(.,
                             objects,
                             by=c("uuidObjectType",
                                  "uuidObject")) %>%
                   select(.,
                          -c(uuidObjectType,
                             uuidObject,
                             number)) %>%
                   left_join(.,
                             measures,
                             by="uuidMeasure") %>%
                   select(.,
                          -c(uuidMeasure,
                             number)) %>%
                   mutate(.,
                          object=description.x,
                          validity=validity,
                          measure=description.y,
                          measurementValue=measurementValue,
                          .keep="none") %>%
                   distinct(.,
                            object,
                            validity,
                            measure,
                            .keep_all=TRUE) %>%
                   pivot_wider(.,
                               names_from=measure,
                               values_from=measurementValue,
                               values_fill=NA)

write.table(event_records,
            file=paste0("event_records_",
                        start_time,
                        "_",
                        end_time,
                        ".csv"),
            append=FALSE,
            quote=FALSE,
            sep=";",
            row.names=FALSE,
            col.names=TRUE)
```

Calculate sample models (THIS PART IS NOT YET SEMANTICALLY NEUTRAL BUT THE IDEA IS TO USE UUIDs INSTEAD OF PARAMETER NAMES AND TO AUTOMATE THE MEASURE SELECTION!)

```{r}
#impact of US governor party affiliation on transit mobility, using reproduction number
model_data <- event_records %>%
                filter(.,
                       str_detect(object,
                                  regex("^state_us_"))) %>%
                select(.,
                       cep_repronum_numeric,
                       leader_party_nominal,
                       c3_Google_TransitStationsMobility_index) %>%
                .[which(complete.cases(.)),]
model_data[which(model_data$leader_party_nominal>1),]$leader_party_nominal <- 0

model <- lm(c3_Google_TransitStationsMobility_index ~.,
            data=model_data)
summary(model)
model_data$leader_party_nominal <- as.factor(model_data$leader_party_nominal)
plot <- ggplot(model_data,
               aes(x=cep_repronum_numeric,
                   y=c3_Google_TransitStationsMobility_index)) +
          geom_point() +
          xlim(0,3) +
          theme_light() +
          theme(legend.position=c(0.8, 0.2),
                legend.background=element_rect(fill="lightgrey"))
ggsave("transit_no_party.tiff",
       plot=plot,
       device="tiff",
       scale=1,
       width=210,
       height=210,
       units="mm",
       dpi=300)
plot <- ggplot(model_data,
               aes(x=cep_repronum_numeric,
                   y=c3_Google_TransitStationsMobility_index,
                   shape=leader_party_nominal,
                   color=leader_party_nominal)) +
          geom_point() +
          xlim(0,3) +
          theme_light() +
          theme(legend.position=c(0.8, 0.2),
                legend.background=element_rect(fill="lightgrey"))
ggsave("transit_party.tiff",
       plot=plot,
       device="tiff",
       scale=1,
       width=210,
       height=210,
       units="mm",
       dpi=300)

#impact of US governor party affiliation on parks mobility, using reproduction number
model_data <- event_records %>%
                filter(.,
                       str_detect(object,
                                  regex("^state_us_"))) %>%
                select(.,
                       cep_repronum_numeric,
                       leader_party_nominal,
                       c3_Google_ParksMobility_index) %>%
                .[which(complete.cases(.)),]
model_data[which(model_data$leader_party_nominal>1),]$leader_party_nominal <- 0

model <- lm(c3_Google_ParksMobility_index ~.,
            data=model_data)
summary(model)
model_data$leader_party_nominal <- as.factor(model_data$leader_party_nominal)
plot <- ggplot(model_data,
               aes(x=cep_repronum_numeric,
                   y=c3_Google_ParksMobility_index)) +
          geom_point() +
          xlim(0,3) +
          theme_light() +
          theme(legend.position=c(0.8, 0.2),
                legend.background=element_rect(fill="lightgrey"))
ggsave("parks_no_party.tiff",
       plot=plot,
       device="tiff",
       scale=1,
       width=210,
       height=210,
       units="mm",
       dpi=300)
plot <- ggplot(model_data,
               aes(x=cep_repronum_numeric,
                   y=c3_Google_ParksMobility_index,
                   shape=leader_party_nominal,
                   color=leader_party_nominal)) +
          geom_point() +
          xlim(0,3) +
          theme_light() +
          theme(legend.position=c(0.8, 0.2),
                legend.background=element_rect(fill="lightgrey"))
ggsave("parks_party.tiff",
       plot=plot,
       device="tiff",
       scale=1,
       width=210,
       height=210,
       units="mm",
       dpi=300)

#impact of US governor party affiliation on government response index, using reproduction number
model_data <- event_records %>%
                filter(.,
                       str_detect(object,
                                  regex("^state_us_"))) %>%
                select(.,
                       cep_repronum_numeric,
                       leader_party_nominal,
                       c3_OxCGRT_Policy_GovernmentResponseIndex_mean_of_ordinal) %>%
                .[which(complete.cases(.)),]
model_data[which(model_data$leader_party_nominal>1),]$leader_party_nominal <- 0

model <- lm(c3_OxCGRT_Policy_GovernmentResponseIndex_mean_of_ordinal ~.,
            data=model_data)
summary(model)
model_data$leader_party_nominal <- as.factor(model_data$leader_party_nominal)
plot <- ggplot(model_data,
               aes(x=cep_repronum_numeric,
                   y=c3_OxCGRT_Policy_GovernmentResponseIndex_mean_of_ordinal)) +
          geom_point() +
          xlim(0,3) +
          theme_light() +
          theme(legend.position=c(0.8, 0.2),
                legend.background=element_rect(fill="lightgrey"))
ggsave("response_no_party.tiff",
       plot=plot,
       device="tiff",
       scale=1,
       width=210,
       height=210,
       units="mm",
       dpi=300)
plot <- ggplot(model_data,
               aes(x=cep_repronum_numeric,
                   y=c3_OxCGRT_Policy_GovernmentResponseIndex_mean_of_ordinal,
                   shape=leader_party_nominal,
                   color=leader_party_nominal)) +
          geom_point() +
          xlim(0,3) +
          theme_light() +
          theme(legend.position=c(0.8, 0.2),
                legend.background=element_rect(fill="lightgrey"))
ggsave("response_party.tiff",
       plot=plot,
       device="tiff",
       scale=1,
       width=210,
       height=210,
       units="mm",
       dpi=300)

#impact of US governor party affiliation on government economic support index, using reproduction number
model_data <- event_records %>%
                filter(.,
                       str_detect(object,
                                  regex("^state_us_"))) %>%
                select(.,
                       cep_repronum_numeric,
                       leader_party_nominal,
                       c3_OxCGRT_Policy_EconomicSupportIndex_mean_of_ordinal) %>%
                .[which(complete.cases(.)),]
model_data[which(model_data$leader_party_nominal>1),]$leader_party_nominal <- 0

model <- lm(c3_OxCGRT_Policy_EconomicSupportIndex_mean_of_ordinal ~.,
            data=model_data)
summary(model)
model_data$leader_party_nominal <- as.factor(model_data$leader_party_nominal)
plot <- ggplot(model_data,
               aes(x=cep_repronum_numeric,
                   y=c3_OxCGRT_Policy_EconomicSupportIndex_mean_of_ordinal)) +
          geom_point() +
          xlim(0,3) +
          theme_light() +
          theme(legend.position=c(0.8, 0.2),
                legend.background=element_rect(fill="lightgrey"))
ggsave("support_no_party.tiff",
       plot=plot,
       device="tiff",
       scale=1,
       width=210,
       height=210,
       units="mm",
       dpi=300)
plot <- ggplot(model_data,
               aes(x=cep_repronum_numeric,
                   y=c3_OxCGRT_Policy_EconomicSupportIndex_mean_of_ordinal,
                   shape=leader_party_nominal,
                   color=leader_party_nominal)) +
          geom_point() +
          xlim(0,3) +
          theme_light() +
          theme(legend.position=c(0.8, 0.2),
                legend.background=element_rect(fill="lightgrey"))
ggsave("support_party.tiff",
       plot=plot,
       device="tiff",
       scale=1,
       width=210,
       height=210,
       units="mm",
       dpi=300)
```

Trial-and-error approach

```{r}
outcomes <- c("c3_Google_ResidentialMobility_index",
              "c3_Apple_TransitMobility_index",
              "c3_Google_WorkplacesMobility_index",
              "c3_Google_TransitStationsMobility_index",
              "c3_Apple_WalkingMobility_index",
              "c3_Google_GroceryMobility_index",
              "c3_Apple_DrivingMobility_index",
              "c3_Google_RetailMobility_index",
              "c3_Google_ParksMobility_index",
              "c3_OxCGRT_Policy_StringencyIndex_mean_of_ordinal",
              "c3_OxCGRT_Policy_ContainmentHealthIndex_mean_of_ordinal",
              "c3_OxCGRT_Policy_EconomicSupportIndex_mean_of_ordinal",
              "c3_OxCGRT_Policy_GovernmentResponseIndex_mean_of_ordinal")
health_status <- c("c3_MaleFemaletotal_InternationalCensus_integer",
                   "c3_MortalityRateUnder5International_numeric",
                   "c3_LifeExpectancyInternational_numeric",
                   "oxford_extreme_poverty_tbd",
                   "oxford_aged_65_older_tbd",
                   "oxford_aged_70_older_tbd",
                   "oxford_hospital_beds_per_thousand_tbd",
                   "oxford_male_smokers_tbd",
                   "oxford_cardiovasc_death_rate_tbd",
                   "oxford_life_expectancy_tbd",
                   "oxford_diabetes_prevalence_tbd",
                   "oxford_population_tbd",
                   "oxford_gdp_per_capita_tbd",
                   "oxford_human_development_index_tbd",
                   "oxford_female_smokers_tbd",
                   "oxford_handwashing_facilities_tbd",
                   "oxford_population_density_tbd",
                   "oxford_median_age_tbd")
leader_status <- c("leader_daysSinceStart_integer",
                   "leader_daysToEnd_integer",
                   "leader_percentTerm_numeric",
                   "leader_daysSinceBirth_integer")
epidemic_status <- c("cep_repronum_se_numeric",
                     "cep_JHU_ConfirmedDeaths_change_integer",
                     "c3_JHU_ConfirmedDeaths_integer",
                     "c3_JHU_ConfirmedCases_integer",
                     "cep_JHU_ConfirmedCases_change_integer",
                     "cep_repronum_numeric",
                     "cep_JHU_ConfirmedDeaths_change_by_population_numeric",
                     "oxford_new_deaths_smoothed_tbd",
                     "oxford_total_tests_tbd",
                     "oxford_hosp_patients_tbd",
                     "oxford_new_tests_smoothed_tbd",
                     "oxford_positive_rate_tbd",
                     "oxford_new_deaths_per_million_tbd",
                     "oxford_weekly_hosp_admissions_per_million_tbd",
                     "oxford_total_cases_tbd",
                     "oxford_weekly_icu_admissions_per_million_tbd",
                     "oxford_total_tests_per_thousand_tbd",
                     "oxford_new_cases_per_million_tbd",
                     "oxford_icu_patients_tbd",
                     "cep_JHU_ConfirmedCases_by_population_numeric",
                     "oxford_new_deaths_smoothed_per_million_tbd",
                     "oxford_hosp_patients_per_million_tbd",
                     "oxford_weekly_icu_admissions_tbd",
                     "oxford_total_cases_per_million_tbd",
                     "oxford_weekly_hosp_admissions_tbd",
                     "oxford_total_cases_per_million_tbd",
                     "oxford_new_tests_tbd",
                     "oxford_new_cases_smoothed_per_million_tbd",
                     "oxford_tests_per_case_tbd",
                     "oxford_total_deaths_per_million_tbd",
                     "oxford_new_cases_tbd",
                     "cep_JHU_ConfirmedCases_change_by_population_numeric",
                     "oxford_new_cases_smoothed_tbd",
                     "oxford_new_deaths_tbd",
                     "oxford_new_tests_smoothed_per_thousand_tbd",
                     "oxford_reproduction_rate_tbd",
                     "oxford_total_deaths_tbd")

#model sampling at country level
event_records_country <- event_records[which(str_detect(event_records$object,
                                                        regex("^country_"))),]
model_sampling_country <- expand.grid(epidemic_status,health_status,outcomes)
model_sampling_country <- pbmclapply(1:nrow(model_sampling_country),FUN=function(x) {
  model_data <- cbind(event_records_country[,model_sampling_country[x,1]],
                      event_records_country[,model_sampling_country[x,2]],
                      event_records_country[,model_sampling_country[x,3]]) %>%
                        .[which(complete.cases(.)),]
  if (nrow(model_data)>100) {
    colnames(model_data)[3] <- "y"
    model <- lm(y ~ .,
                data=model_data)
    model <- data.frame(epidemic_status=model_sampling_country[x,1],
                        health_status=model_sampling_country[x,2],
                        outcome=model_sampling_country[x,3],
                        adj_r_squared=summary(model)$adj.r.squared,
                        stringsAsFactors=FALSE)
  } else {
    model <- as.character(NA)
  }
  return(model)
},mc.cores=8L) %>%
  .[which(!(is.na(.)))] %>%
  ldply(.parallel=TRUE) %>%
  mutate(.,
         x=paste0(health_status,
                  "__",
                  epidemic_status),
         y=outcome,
         z=adj_r_squared,
         .keep="none") %>%
  setDT() %>%
  setorder(.,
           -z)
model_sampling_country$x <- factor(model_sampling_country$x,
                                   levels=rev(unique(model_sampling_country$x)))
model_sampling_country$y <- factor(model_sampling_country$y,
                                   levels=rev(unique(model_sampling_country$y)))

#create heatmap for adjusted r-squared
plot <- ggplot(model_sampling_country,
               aes(x,y,fill=z)) +
          geom_tile() +
          scale_x_discrete(name="Health & Epidemic Status",
                           breaks=NULL,
                           labels=NULL) +
          scale_y_discrete(name="Response",
                           breaks=NULL,
                           labels=NULL)
ggsave("response_heatmap.tiff",
       plot=plot,
       device="tiff",
       scale=1,
       width=210,
       height=210,
       units="mm",
       dpi=300)
write.table(model_sampling_country,
            file="response_heatmap.csv",
            append=FALSE,
            quote=FALSE,
            sep=";",
            row.names=FALSE,
            col.names=TRUE)

#correlations health/outcomes
model_sampling_country <- expand.grid(health_status,outcomes)
model_sampling_country <- pbmclapply(1:nrow(model_sampling_country),FUN=function(x) {
  model_data <- cbind(event_records_country[,model_sampling_country[x,1]],
                      event_records_country[,model_sampling_country[x,2]]) %>%
                        .[which(complete.cases(.)),]
  if (nrow(model_data)>100) {
    colnames(model_data) <- c("x",
                              "y")
    cor <- cor(model_data$x,
               model_data$y)
  } else {
    cor=as.numeric(NA)
  }
  model <- data.frame(health_status=model_sampling_country[x,1],
                    outcome=model_sampling_country[x,2],
                    cor=cor,
                    stringsAsFactors=FALSE)
  return(model)
},mc.cores=8L) %>%
  ldply(.parallel=TRUE) %>%
  setDT() %>%
    setorder(.,
             -cor)
model_sampling_country <- model_sampling_country[which(!(is.na(model_sampling_country$cor))),]
model_sampling_country$health_status <- factor(model_sampling_country$health_status,
                                               levels=rev(unique(model_sampling_country$health_status)))
model_sampling_country$outcome <- factor(model_sampling_country$outcome,
                                         levels=rev(unique(model_sampling_country$outcome)))

#create heatmap for correlation
plot <- ggplot(model_sampling_country,
               aes(health_status,outcome,fill=cor)) +
          geom_tile() +
          scale_x_discrete(name="Health Status",
                           breaks=NULL,
                           labels=NULL) +
          scale_y_discrete(name="Response",
                           breaks=NULL,
                           labels=NULL)
ggsave("response_cor_st_heatmap.tiff",
       plot=plot,
       device="tiff",
       scale=1,
       width=210,
       height=210,
       units="mm",
       dpi=300)
write.table(model_sampling_country,
            file="response_cor_st_heatmap.csv",
            append=FALSE,
            quote=FALSE,
            sep=";",
            row.names=FALSE,
            col.names=TRUE)

#correlations epidemic/outcomes
model_sampling_country <- expand.grid(epidemic_status,outcomes)
model_sampling_country <- pbmclapply(1:nrow(model_sampling_country),FUN=function(x) {
  model_data <- cbind(event_records_country[,model_sampling_country[x,1]],
                      event_records_country[,model_sampling_country[x,2]]) %>%
                        .[which(complete.cases(.)),]
  if (nrow(model_data)>100) {
    colnames(model_data) <- c("x",
                              "y")
    cor <- cor(model_data$x,
               model_data$y)
  } else {
    cor=as.numeric(NA)
  }
  model <- data.frame(epidemic_status=model_sampling_country[x,1],
                    outcome=model_sampling_country[x,2],
                    cor=cor,
                    stringsAsFactors=FALSE)
  return(model)
},mc.cores=8L) %>%
  ldply(.parallel=TRUE) %>%
    setDT() %>%
    setorder(.,
             -cor)
model_sampling_country <- model_sampling_country[which(!(is.na(model_sampling_country$cor))),]
model_sampling_country$epidemic_status <- factor(model_sampling_country$epidemic_status,
                                                 levels=rev(unique(model_sampling_country$epidemic_status)))
model_sampling_country$outcome <- factor(model_sampling_country$outcome,
                                         levels=rev(unique(model_sampling_country$outcome)))

#create heatmap for correlation
plot <- ggplot(model_sampling_country,
               aes(epidemic_status,outcome,fill=cor)) +
          geom_tile() +
          scale_x_discrete(name="Epidemic Status",
                           breaks=NULL,
                           labels=NULL) +
          scale_y_discrete(name="Response",
                           breaks=NULL,
                           labels=NULL)
ggsave("response_cor_ep_heatmap.tiff",
       plot=plot,
       device="tiff",
       scale=1,
       width=210,
       height=210,
       units="mm",
       dpi=300)
write.table(model_sampling_country,
            file="response_cor_ep_heatmap.csv",
            append=FALSE,
            quote=FALSE,
            sep=";",
            row.names=FALSE,
            col.names=TRUE)

model_final <- lm(c3_Apple_TransitMobility_index ~ oxford_aged_70_older_tbd + oxford_aged_65_older_tbd + oxford_median_age_tbd + 	
oxford_tests_per_case_tbd + oxford_new_tests_smoothed_per_thousand_tbd + oxford_total_tests_per_thousand_tbd,data=event_records_country)

event_records_country$validity <- date(substr(event_records_country$validity,
                                              nchar(event_records_country$validity)-22,
                                              nchar(event_records_country$validity)))
event_records_country_estimate <- event_records_country[which(event_records_country$validity<=date("2020-06-06")),]
event_records_country_test <- event_records_country[which(event_records_country$validity>date("2020-06-06")),]

model_estimate <- lm(c3_Apple_TransitMobility_index ~ oxford_aged_70_older_tbd + oxford_aged_65_older_tbd + oxford_median_age_tbd + 	
oxford_tests_per_case_tbd + oxford_new_tests_smoothed_per_thousand_tbd + oxford_total_tests_per_thousand_tbd,data=event_records_country_estimate)

prediction <- predict(model_estimate,
                      event_records_country_test)
cor(prediction,event_records_country_test$c3_Apple_TransitMobility_index,use="pairwise.complete.obs")
```
