---
title: "C3.ai measureID creation notebook"
output: html_notebook
---

# C3.ai COVID-19 Data Lake - MeasureID Creation

This notebook creates UUIDs for the measures that are meant to be acquired from C3.ai's data lake.

To view an outline of this notebook, use the RStudio keyboard shortcut Control + Shift + O on Windows or Command + Shift + O on Mac. 

Remark: Some of the packages may not be needed, use the following (sample) code to load packages instead:

#define a function to install and load required packages
ipak <- function(pkg){
  new.pkg <- pkg[!(pkg %in% installed.packages()[, "Package"])]
  if (length(new.pkg)) 
    install.packages(new.pkg, dependencies = TRUE)
  sapply(pkg, require, character.only = TRUE)
}

#specify a list of required packages
pack_list <- c("dplyr",
               "lubridate",
               "NCmisc")

#install and load packages
suppressWarnings(ipak(pack_list))

#define current working directory
current_wd <- dirname(rstudioapi::getActiveDocumentContext()$path)
setwd(current_wd)

#cross-check unused packages
used_packages <- list.functions.in.file(rstudioapi::getSourceEditorContext()$path) %>%
  names() %>%
  unique()
pack_list <- paste0("package:",unlist(pack_list))
print("Unused packages:")
print(setdiff(pack_list,used_packages))
print("Missing packages:")
print(setdiff(used_packages,pack_list))

```{r}
if (!require(plyr)) install.packages('plyr')
if (!require(tidyverse)) install.packages('tidyverse')
if (!require(httr)) install.packages('httr')
if (!require(jsonlite)) install.packages('jsonlite')
if (!require(zoo)) install.packages('zoo')
if (!require(lubridate)) install.packages('lubridate')
if (!require(uuid)) install.packages('uuid')
if (!require(pbmcapply)) install.packages('pbmcapply')
if (!require(readxl)) install.packages('readxl')

library(plyr)
library(tidyverse)
library(httr)
library(jsonlite)
library(zoo)
library(lubridate)
library(uuid)
library(pbmcapply)
library(readxl)
```

Define measures and assign UUIDs.

```{r}
measureIDs <- c("Apple_WalkingMobility", 
                "Apple_DrivingMobility",
                "Apple_TransitMobility",
                "Google_ParksMobility",
                "Google_ResidentialMobility",
                "Google_RetailMobility",
                "Google_GroceryMobility",
                "Google_TransitStationsMobility",
                "Google_WorkplacesMobility",
                "OxCGRT_Policy_C1_Flag",
                "OxCGRT_Policy_C1_SchoolClosing",
                "OxCGRT_Policy_C8_InternationalTravelControls",
                "OxCGRT_Policy_E1_IncomeSupport",
                "OxCGRT_Policy_ConfirmedCases",
                "OxCGRT_Policy_ConfirmedDeaths",
                "OxCGRT_Policy_StringencyIndex",
                "OxCGRT_Policy_StringencyIndexForDisplay",
                "OxCGRT_Policy_StringencyLegacyIndex",
                "OxCGRT_Policy_StringencyLegacyIndexForDisplay",
                "OxCGRT_Policy_GovernmentResponseIndex",
                "OxCGRT_Policy_GovernmentResponseIndexForDisplay",
                "OxCGRT_Policy_ContainmentHealthIndex",
                "OxCGRT_Policy_ContainmentHealthIndexForDisplay",
                "OxCGRT_Policy_EconomicSupportIndex",
                "OxCGRT_Policy_EconomicSupportIndexForDisplay",
                "JHU_ConfirmedCases",
                "JHU_ConfirmedDeaths",
                "LifeExpectancyInternational",
                "MaleFemaletotal_InternationalCensus",
                "MortalityRateUnder5International")
measureScales <- c("index",  
                   "index",
                   "index",
                   "index",
                   "index",
                   "index",
                   "index",
                   "index",
                   "index",
                   "binary",
                   "ordinal",
                   "ordinal",
                   "ordinal",
                   "integer",
                   "integer",
                   "mean_of_ordinal",
                   "mean_of_ordinal",
                   "mean_of_ordinal",
                   "mean_of_ordinal",
                   "mean_of_ordinal",
                   "mean_of_ordinal",
                   "mean_of_ordinal",
                   "mean_of_ordinal",
                   "mean_of_ordinal",
                   "mean_of_ordinal",
                   "integer",
                   "integer",
                   "numeric",
                   "integer",
                   "numeric")
measureIDs <- data.frame(source="c3",
                         uuidMeasure=UUIDgenerate(n=length(measureIDs)),
                         description=measureIDs,
                         scaleLevel=measureScales,
                         stringsAsFactors=FALSE) %>%
                mutate(.,
                       source=as.factor(source),
                       uuidMeasure=as.factor(uuidMeasure),
                       scaleLevel=as.factor(scaleLevel))
write.table(measureIDs,
            file="events/measureIDs.csv",
            append=FALSE,
            quote=FALSE,
            sep=";",
            row.names=FALSE,
            col.names=TRUE)
```
