---
title: "C3.ai objectID creation notebook"
output: html_notebook
---

# C3.ai COVID-19 Data Lake - ObjectID Creation

This R notebook fetches IDs for countries, US states and German states, and assigns UUIDs to these objects and the respective object types (type of geographical entity)

To view an outline of this notebook, use the RStudio keyboard shortcut Control + Shift + O on Windows or Command + Shift + O on Mac. 

Remark: Some of the packages may not be needed, use the following (sample) code to load packages instead:

#define a function to install and load required packages
ipak <- function(pkg){
  new.pkg <- pkg[!(pkg %in% installed.packages()[, "Package"])]
  if (length(new.pkg)) 
    install.packages(new.pkg, dependencies = TRUE)
  sapply(pkg, require, character.only = TRUE)
}

#specify a list of required packages
pack_list <- c("dplyr",
               "lubridate",
               "NCmisc")

#install and load packages
suppressWarnings(ipak(pack_list))

#define current working directory
current_wd <- dirname(rstudioapi::getActiveDocumentContext()$path)
setwd(current_wd)

#cross-check unused packages
used_packages <- list.functions.in.file(rstudioapi::getSourceEditorContext()$path) %>%
  names() %>%
  unique()
pack_list <- paste0("package:",unlist(pack_list))
print("Unused packages:")
print(setdiff(pack_list,used_packages))
print("Missing packages:")
print(setdiff(used_packages,pack_list))

```{r}
if (!require(plyr)) install.packages('plyr')
if (!require(tidyverse)) install.packages('tidyverse')
if (!require(httr)) install.packages('httr')
if (!require(jsonlite)) install.packages('jsonlite')
if (!require(zoo)) install.packages('zoo')
if (!require(lubridate)) install.packages('lubridate')
if (!require(uuid)) install.packages('uuid')
if (!require(pbmcapply)) install.packages('pbmcapply')
if (!require(readxl)) install.packages('readxl')

library(plyr)
library(tidyverse)
library(httr)
library(jsonlite)
library(zoo)
library(lubridate)
library(uuid)
library(pbmcapply)
library(readxl)
```

## Helper methods for accessing the API

The helper methods in `c3aidatalake.R` convert a JSON response from the C3.ai APIs to a Tibble. You may wish to view the code in `c3aidatalake.R` before continuing.

```{r}
source("c3aidatalake.R")
```

Get all countries; remark: countries are missing (because they are not identified as "countries")

Germany is missing and therefore added manually (as data for Germany are available)

```{r}
countries <- fetch(
    "outbreaklocation",
    list(
      spec = list(
        filter = "locationType == 'country'"
      )
    ),
    get_all = TRUE
) %>% 
  select(locationType,id)

countries <- rbind(countries,
                   c(locationType="country",
                     id="Germany"))
countries
```

Get all US states; remark: states are missing (because they are not identified as states and ambiguous - like "Pennsylvania_USA" and "Pennsylvania_UnitedStates", same with
3 different variants for New Jersey)

```{r}
states_us <- fetch(
    "outbreaklocation",
    list(
      spec = list(
        filter = "contains(id, 'UnitedStates') && locationType == 'state'"
      )
    ),
    get_all = TRUE
) %>% 
  select(-location) %>% 
  unnest_wider(fips, names_sep = ".") %>% 
  select(id) %>%
  cbind(locationType="state_us",.)

states_us
```

Get all German states

Berlin is missing and therefore added manually

```{r}
states_de <- fetch(
    "outbreaklocation",
    list(
      spec = list(
        filter = "contains(id, 'Germany') && locationType == 'state'"
      )
    ),
    get_all = TRUE
) %>% 
  select(id) %>%
  cbind(locationType="state_de",.)

states_de <- rbind(states_de,
                   c(locationType="state_de",
                     id="Berlin_Germany"))
states_de
```

Consolidate/standardize objectIDs

```{r}
objectIDs <- rbind(countries,
                   states_us,
                   states_de)
objectTypeIDs <- data.frame(uuidObjectType=UUIDgenerate(n=length(unique(objectIDs$locationType))),
                            description=unique(objectIDs$locationType),
                            stringsAsFactors=FALSE) %>%
                   mutate(.,
                          uuidObjectType=as.factor(uuidObjectType))
write.table(objectTypeIDs,
            file="events/objectTypeIDs.csv",
            append=FALSE,
            quote=FALSE,
            sep=";",
            row.names=FALSE,
            col.names=TRUE)

objectIDs <- mutate(objectIDs,
                    description=id) %>%
               left_join(.,
                         objectTypeIDs,
                         by=c("locationType"="description")) %>%
               group_by(description) %>%
               unique(.) %>%
               cbind(uuidObject=UUIDgenerate(n=nrow(.)),.) %>%
               select(uuidObjectType,
                      uuidObject,
                      description) %>%
               mutate(.,
                      uuidObjectType=as.factor(uuidObjectType),
                      uuidObject=as.factor(uuidObject))
write.table(objectIDs,
            file="events/objectIDs.csv",
            append=FALSE,
            quote=FALSE,
            sep=";",
            row.names=FALSE,
            col.names=TRUE)
```
