---
title: "C3.ai ISO objectID notebook"
output: html_notebook
---

# C3.ai COVID-19 Data Lake - ISO objectID

Many data sources use ISO codes instead of C3's "outbreak location" to identify countries or lower-level geographical entities (like states); to be able to integrate Oxford test data, we will at least need ISO codes at country level. This notebook produces a file that needs to be reviewed manually for further processing (as not all countries can be assigned manually)

To view an outline of this notebook, use the RStudio keyboard shortcut Control + Shift + O on Windows or Command + Shift + O on Mac.

Remark: Some of the packages may not be needed, use the following (sample) code to load packages instead:

#define a function to install and load required packages
ipak <- function(pkg){
  new.pkg <- pkg[!(pkg %in% installed.packages()[, "Package"])]
  if (length(new.pkg)) 
    install.packages(new.pkg, dependencies = TRUE)
  sapply(pkg, require, character.only = TRUE)
}

#specify a list of required packages
pack_list <- c("dplyr",
               "lubridate",
               "NCmisc")

#install and load packages
suppressWarnings(ipak(pack_list))

#define current working directory
current_wd <- dirname(rstudioapi::getActiveDocumentContext()$path)
setwd(current_wd)

#cross-check unused packages
used_packages <- list.functions.in.file(rstudioapi::getSourceEditorContext()$path) %>%
  names() %>%
  unique()
pack_list <- paste0("package:",unlist(pack_list))
print("Unused packages:")
print(setdiff(pack_list,used_packages))
print("Missing packages:")
print(setdiff(used_packages,pack_list))

```{r}
if (!require(plyr)) install.packages('plyr')
if (!require(tidyverse)) install.packages('tidyverse')
if (!require(httr)) install.packages('httr')
if (!require(jsonlite)) install.packages('jsonlite')
if (!require(zoo)) install.packages('zoo')
if (!require(lubridate)) install.packages('lubridate')
if (!require(uuid)) install.packages('uuid')
if (!require(pbmcapply)) install.packages('pbmcapply')
if (!require(readxl)) install.packages('readxl')
if (!require(jsonlite)) install.packages('jsonlite')
if (!require(ISOcodes)) install.packages('ISOcodes')

library(plyr)
library(tidyverse)
library(httr)
library(jsonlite)
library(zoo)
library(lubridate)
library(uuid)
library(pbmcapply)
library(readxl)
library(jsonlite)
library(ISOcodes)
```

Get existing object IDs for countries

```{r}
objectTypeIDs <- read.csv("events/objectTypeIDs.csv",
                          header=TRUE,
                          sep=";")
objectIDs <- read.csv("events/objectIDs.csv",
                    header=TRUE,
                    sep=";")
objectIDs_countries <- left_join(objectIDs,
                                 objectTypeIDs,
                                 by="uuidObjectType") %>%
                         .[which(.$description.y=="country"),] %>%
                         select(.,
                                -description.y) %>%
                         mutate(.,
                                description=description.x,
                                .keep="unused")
```

Add ISO codes to country list

```{r}
objectIDs_iso <- left_join(objectIDs_countries,
                           ISO_3166_1,
                           by=c("description"="Name"),
                           keep=TRUE) %>%
                   select(.,
                          c(uuidObjectType,
                            uuidObject,
                            description,
                            Alpha_3))
write.table(objectIDs_iso,
            file="events/objectIDs_iso_for_review.csv",
            append=FALSE,
            quote=FALSE,
            sep=";",
            na="",
            row.names=FALSE,
            col.names=TRUE)
```

At this stage, the list of ISO codes needs to be manually reviewed/amended. It will then be merged with the list of objectIDs.

