---
title: "C3.ai add ISO codes"
output: html_notebook
---

# C3.ai COVID-19 Data Lake - Add ISO Codes

This notebook uses the manually reviewed ISO codes and adds this information to existing object IDs. Due to inconsistencies, some object IDs will not have ISO codes (Sao Tome for example appeared more than once in C3's list of countries, MetropolitanFrance is not a country, etc.).

To view an outline of this notebook, use the RStudio keyboard shortcut Control + Shift + O on Windows or Command + Shift + O on Mac.

Remark: Some of the packages may not be needed, use the following (sample) code to load packages instead:

#define a function to install and load required packages
ipak <- function(pkg){
  new.pkg <- pkg[!(pkg %in% installed.packages()[, "Package"])]
  if (length(new.pkg)) 
    install.packages(new.pkg, dependencies = TRUE)
  sapply(pkg, require, character.only = TRUE)
}

#specify a list of required packages
pack_list <- c("dplyr",
               "lubridate",
               "NCmisc")

#install and load packages
suppressWarnings(ipak(pack_list))

#define current working directory
current_wd <- dirname(rstudioapi::getActiveDocumentContext()$path)
setwd(current_wd)

#cross-check unused packages
used_packages <- list.functions.in.file(rstudioapi::getSourceEditorContext()$path) %>%
  names() %>%
  unique()
pack_list <- paste0("package:",unlist(pack_list))
print("Unused packages:")
print(setdiff(pack_list,used_packages))
print("Missing packages:")
print(setdiff(used_packages,pack_list))

```{r}
if (!require(plyr)) install.packages('plyr')
if (!require(tidyverse)) install.packages('tidyverse')
if (!require(httr)) install.packages('httr')
if (!require(jsonlite)) install.packages('jsonlite')
if (!require(zoo)) install.packages('zoo')
if (!require(lubridate)) install.packages('lubridate')
if (!require(uuid)) install.packages('uuid')
if (!require(pbmcapply)) install.packages('pbmcapply')
if (!require(readxl)) install.packages('readxl')
if (!require(jsonlite)) install.packages('jsonlite')
if (!require(ISOcodes)) install.packages('ISOcodes')

library(plyr)
library(tidyverse)
library(httr)
library(jsonlite)
library(zoo)
library(lubridate)
library(uuid)
library(pbmcapply)
library(readxl)
library(jsonlite)
library(ISOcodes)
```

Get existing object IDs and add manually reviewed ISO codes

```{r}
objectIDs <- read.csv("events/objectIDs.csv",
                    header=TRUE,
                    sep=";")
objectIDs_iso_reviewed <- read.csv("events/objectIDs_iso_reviewed.csv",
                                   header=TRUE,
                                   sep=";")
objectIDs <- left_join(objectIDs,
                       objectIDs_iso_reviewed,
                       by=c("uuidObjectType","uuidObject")) %>%
               mutate(.,
                      description=description.x,
                      iso=Alpha_3,
                      .keep="unused") %>%
               select(.,
                      -description.y)
```

Save enriched objectIDs

```{r}
write.table(objectIDs,
            file="events/objectIDs.csv",
            append=FALSE,
            quote=FALSE,
            sep=";",
            na="",
            row.names=FALSE,
            col.names=TRUE)
```
