---
title: "C3.ai C3 data abstraction notebook"
output: html_notebook
---

# C3.ai COVID-19 Data Lake - C3 Data Abstraction

This notebook acquires time series from the C3.ai data lake and stores them in an abstraction layer as event types.

For the time being, we are using a simplified model in which only the data segment but not the header segment will be created for event types.

To view an outline of this notebook, use the RStudio keyboard shortcut Control + Shift + O on Windows or Command + Shift + O on Mac. 

Remark: Some of the packages may not be needed, use the following (sample) code to load packages instead:

#define a function to install and load required packages
ipak <- function(pkg){
  new.pkg <- pkg[!(pkg %in% installed.packages()[, "Package"])]
  if (length(new.pkg)) 
    install.packages(new.pkg, dependencies = TRUE)
  sapply(pkg, require, character.only = TRUE)
}

#specify a list of required packages
pack_list <- c("dplyr",
               "lubridate",
               "NCmisc")

#install and load packages
suppressWarnings(ipak(pack_list))

#define current working directory
current_wd <- dirname(rstudioapi::getActiveDocumentContext()$path)
setwd(current_wd)

#cross-check unused packages
used_packages <- list.functions.in.file(rstudioapi::getSourceEditorContext()$path) %>%
  names() %>%
  unique()
pack_list <- paste0("package:",unlist(pack_list))
print("Unused packages:")
print(setdiff(pack_list,used_packages))
print("Missing packages:")
print(setdiff(used_packages,pack_list))

```{r}
if (!require(plyr)) install.packages('plyr')
if (!require(tidyverse)) install.packages('tidyverse')
if (!require(httr)) install.packages('httr')
if (!require(jsonlite)) install.packages('jsonlite')
if (!require(zoo)) install.packages('zoo')
if (!require(lubridate)) install.packages('lubridate')
if (!require(uuid)) install.packages('uuid')
if (!require(pbmcapply)) install.packages('pbmcapply')
if (!require(readxl)) install.packages('readxl')

library(plyr)
library(tidyverse)
library(httr)
library(jsonlite)
library(zoo)
library(lubridate)
library(uuid)
library(pbmcapply)
library(readxl)
```

## Helper methods for accessing the API

The helper methods in `c3aidatalake.R` convert a JSON response from the C3.ai APIs to a Tibble. You may wish to view the code in `c3aidatalake.R` before continuing.

```{r}
source("c3aidatalake.R")
```

Load event type definitions (object types, objects, measures)

```{r}
objectTypeIDs <- read.csv(file="events/objectTypeIDs.csv",
                          header=TRUE,
                          sep=";")
print(paste0("Loaded ",
             nrow(objectTypeIDs),
             " objectTypeIDs"))
str(objectTypeIDs)
objectIDs <- read.csv(file="events/objectIDs.csv",
                      header=TRUE,
                      sep=";") %>%
               .[which(!(is.na(.$description))),] %>%
               .[which(!(.$description=="")),]
print(paste0("Loaded ",
             nrow(objectIDs),
             " objectIDs"))
str(objectIDs)
measureIDs <- read.csv(file="events/measureIDs.csv",
                      header=TRUE,
                      sep=";") %>%
                .[which(.$source=="c3"),]
print(paste0("Loaded ",
             nrow(measureIDs),
             " C3 measureIDs"))
str(measureIDs)
```

Define function to split off measureIDs, streamline and save event data

```{r}
save_events <- function (data) {
  print(paste0(length(unique(data$name)),
               " objects received"))
  print(paste0(length(unique(data$value_id)),
               " measures received"))
  data <- left_join(data,
                    objectIDs,
                    by=c("name"="description")) %>%
          left_join(.,
                    measureIDs,
                    by=c("value_id"="description")) %>%
          select(uuidObjectType,
                 uuidObject,
                 uuidMeasure,
                 dates,
                 data)
  data$eventType <- paste0(data$uuidObjectType,
                           "_",
                           data$uuidMeasure)
  colnames(data)[4:5] <- c("measurementTime",
                           "measurementValue")
  data$measurementValue <- as.character(data$measurementValue)
  data <- select(data,
                 eventType,
                 uuidObject,
                 measurementTime,
                 measurementValue)
  
  #function to save data by event type
  save_group <- function(data,
                         eventType) {
    save(data,
         file=paste0("events/",
                     eventType,
                     ".rda"))
  }
  
  print(paste0(length(unique(data$eventType)),
               " event types identified"))
  
  data %>%
    mutate(.,
           uuidObject=as.factor(uuidObject)) %>%
    group_by(eventType) %>%
    group_walk(~ save_group(.x,
                            .y$eventType))
}
```

Get and save mobility data

```{r}
end_date <- Sys.Date()

data <- evalmetrics(
  "outbreaklocation",
  list(
    spec = list(
      ids = objectIDs$description,
      expressions = list(
        "Apple_WalkingMobility", 
        "Apple_DrivingMobility",
        "Apple_TransitMobility",
        "Google_ParksMobility",
        "Google_ResidentialMobility",
        "Google_RetailMobility",
        "Google_GroceryMobility",
        "Google_TransitStationsMobility",
        "Google_WorkplacesMobility"
      ),
      start = "2020-02-15",
      end = end_date,
      interval = "DAY"
    )
  ),
  get_all = TRUE
) %>% 
  filter(missing == 0) %>% 
  select(-missing)

#save mobility data
save_events(data)
```

Get and save detailed policy data

```{r}
data_types <- c("OxCGRT_Policy_C1_Flag",
                "OxCGRT_Policy_C1_SchoolClosing",
                "OxCGRT_Policy_C8_InternationalTravelControls",
                "OxCGRT_Policy_E1_IncomeSupport",
                "OxCGRT_Policy_ConfirmedCases",
                "OxCGRT_Policy_ConfirmedDeaths",
                "OxCGRT_Policy_StringencyIndex",
                "OxCGRT_Policy_StringencyIndexForDisplay",
                "OxCGRT_Policy_StringencyLegacyIndex",
                "OxCGRT_Policy_StringencyLegacyIndexForDisplay",
                "OxCGRT_Policy_GovernmentResponseIndex",
                "OxCGRT_Policy_GovernmentResponseIndexForDisplay",
                "OxCGRT_Policy_ContainmentHealthIndex",
                "OxCGRT_Policy_ContainmentHealthIndexForDisplay",
                "OxCGRT_Policy_EconomicSupportIndex",
                "OxCGRT_Policy_EconomicSupportIndexForDisplay")

end_date <- Sys.Date()

for (i in 1:length(data_types)) {
  data <- evalmetrics(
    "outbreaklocation",
    list(
      spec = list(
        ids = objectIDs$description,
        expressions = data_types[i],
        start = "2020-02-15",
        end = end_date,
        interval = "DAY"
      )
    ),
    get_all = TRUE
  ) %>% 
    filter(missing == 0) %>% 
    select(-missing)
  
  #save oxford data
  save_events(data)
  print(paste0("Oxford processed: ",
               i,
               " of ",
               length(data_types)))
}
```

Get JHU Data (Recoveries not used, no data)

```{r}
data_types <- c("JHU_ConfirmedCases",
                "JHU_ConfirmedDeaths")

end_date <- Sys.Date()

for (i in 1:length(data_types)) {
  data <- evalmetrics(
    "outbreaklocation",
    list(
      spec = list(
        ids = objectIDs$description,
        expressions = data_types[i],
        start = "2020-02-15",
        end = end_date,
        interval = "DAY"
      )
    ),
    get_all = TRUE
  ) %>% 
    filter(missing == 0) %>% 
    select(-missing)
  
  #save jhu data
  save_events(data)
  print(paste0("JHU processed ",
               i,
               " of ",
               length(data_types)))
}
```

Get and save international census data

```{r}
data_types <- c("LifeExpectancyInternational",
                "MaleFemaletotal_InternationalCensus",
                "MortalityRateUnder5International")

end_date <- Sys.Date()

for (i in 1:length(data_types)) {
  data <- evalmetrics(
    "outbreaklocation",
    list(
      spec = list(
        ids = objectIDs$description,
        expressions = data_types[i],
        start = "2020-02-15",
        end = end_date,
        interval = "DAY"
      )
    ),
    get_all = TRUE
  ) %>% 
    filter(missing == 0) %>% 
    select(-missing)

  #save census data
  save_events(data)
  print(paste0("International census processed ",
               i,
               " of ",
               length(data_types)))
}
```
