---
title: "C3.ai Oxford data abstraction notebook"
output: html_notebook
---

# C3.ai COVID-19 Data Lake - Oxford Data Abstraction

This notebook acquires time series from Oxford test data and stores them in an abstraction layer as event types.

For the time being, we are using a simplified model in which only the data segment but not the header segment will be created for event types.

To view an outline of this notebook, use the RStudio keyboard shortcut Control + Shift + O on Windows or Command + Shift + O on Mac.

Remark: Some of the packackes may not be needed, use the following (sample) code to load packages instead:

#define a function to install and load required packages
ipak <- function(pkg){
  new.pkg <- pkg[!(pkg %in% installed.packages()[, "Package"])]
  if (length(new.pkg)) 
    install.packages(new.pkg, dependencies = TRUE)
  sapply(pkg, require, character.only = TRUE)
}

#specify a list of required packages
pack_list <- c("dplyr",
               "lubridate",
               "NCmisc")

#install and load packages
suppressWarnings(ipak(pack_list))

#define current working directory
current_wd <- dirname(rstudioapi::getActiveDocumentContext()$path)
setwd(current_wd)

#cross-check unused packages
used_packages <- list.functions.in.file(rstudioapi::getSourceEditorContext()$path) %>%
  names() %>%
  unique()
pack_list <- paste0("package:",unlist(pack_list))
print("Unused packages:")
print(setdiff(pack_list,used_packages))
print("Missing packages:")
print(setdiff(used_packages,pack_list))

```{r}
if (!require(plyr)) install.packages('plyr')
if (!require(tidyverse)) install.packages('tidyverse')
if (!require(httr)) install.packages('httr')
if (!require(jsonlite)) install.packages('jsonlite')
if (!require(zoo)) install.packages('zoo')
if (!require(lubridate)) install.packages('lubridate')
if (!require(uuid)) install.packages('uuid')
if (!require(pbmcapply)) install.packages('pbmcapply')
if (!require(readxl)) install.packages('readxl')
if (!require(jsonlite)) install.packages('jsonlite')
if (!require(purrr)) install.packages('purrr')

library(plyr)
library(tidyverse)
library(httr)
library(jsonlite)
library(zoo)
library(lubridate)
library(uuid)
library(pbmcapply)
library(readxl)
library(jsonlite)
library(purrr)
```

Get oxford data

```{r}
objectIDs <- read.csv(file="events/objectIDs.csv",
                      header=TRUE,
                      sep=";") %>%
               .[which(!(is.na(.$iso))),] %>%
               .[which(!(.$iso=="")),]
measureIDs <- read.csv(file="events/measureIDs.csv",
                       header=TRUE,
                       sep=";") %>%
                .[which(.$source=="oxford"),]
                
#get Oxford data, save as .csv file
oxford_data <- read.csv(file="https://covid.ourworldindata.org/data/owid-covid-data.csv",
                        header=TRUE,
                        sep=",",
                        dec=".") %>%
                 mutate(.,
                        date=as.POSIXct(paste0(date,
                                               " 00:00:00 GMT"))) %>%
                 mutate(.,
                        date=with_tz(date,
                                     tzone="UTC")) %>%
                 .[order(.$date),]
save(oxford_data,
     file="events/oxford_data_csv.rda")

#ensure that there are records for each combination of iso and date (assuming that no dates are missing between min and max of original data)
oxford_data <- expand.grid(unique(oxford_data$iso_code),
                           unique(oxford_data$date)) %>%
                 left_join(.,
                           oxford_data,
                           by=c("Var1"="iso_code",
                                "Var2"="date"))
colnames(oxford_data)[1:2] <- c("iso_code",
                                "date")

#fill in missing data for stable variables
oxford_data <- oxford_data %>%
                 group_by(.,iso_code) %>%
                 fill(.,
                      c("population":"human_development_index"),
                      .direction=c("downup")) %>%
                 ungroup()

#consider only data with existing object IDs and same test units
oxford_data <- oxford_data[which(oxford_data$iso_code %in% objectIDs$iso),]
total_tests_col <- which(colnames(oxford_data)=="total_tests")
positive_rate_col <- which(colnames(oxford_data)=="positive_rate")
oxford_data[which(!(oxford_data$tests_units %in% c("people tested",
                                                  "people tested (incl. non-PCR)",
                                                  ""))),total_tests_col:positive_rate_col] <- as.numeric(NA)

#consider only known measures
oxford_data <- oxford_data[,which(names(oxford_data) %in% c("iso_code",
                                                            "date",
                                                            measureIDs$description))] %>%
                 left_join(.,
                           objectIDs,
                           by=c("iso_code"="iso")) %>%
                 select(.,
                        -iso_code)

#prepare event-based format
oxford_data <- pivot_longer(oxford_data,
                            cols=measureIDs$description,
                            names_to="measurement_description",
                            values_to="measurementValue") %>%
                 na.omit(.,
                         measurementValue) %>%
                 left_join(.,
                           measureIDs,
                           by=c("measurement_description"="description")) %>%
                 mutate(.,
                        eventType=paste0(uuidObjectType,
                                         "_",
                                         uuidMeasure),
                        uuidObject=as.factor(uuidObject),
                        measurementTime=date,
                        measurementValue=as.character(measurementValue)) %>%
                 select(.,
                        c(eventType,
                          uuidObject,
                          measurementTime,
                          measurementValue))

#function to save data by event type
save_group <- function(data,
                       eventType) {
  save(data,
       file=paste0("events/",
                   eventType,
                   ".rda"))
}
  
#save data  
oxford_data %>%
  group_by(eventType) %>%
  group_walk(~ save_group(.x,
                          .y$eventType))
```
