---
title: "C3.ai German states prime minister data abstraction notebook"
output: html_notebook
---

# C3.ai COVID-19 Data Lake - German States Prime Ministers Data Abstraction

This notebook acquires data about the prime ministers of German states and stores them in an abstraction layer as event types.

For the time being, we are using a simplified model in which only the data segment but not the header segment will be created for event types.

To view an outline of this notebook, use the RStudio keyboard shortcut Control + Shift + O on Windows or Command + Shift + O on Mac.

Remark: Some of the packages may not be needed, use the following (sample) code to load packages instead:

#define a function to install and load required packages
ipak <- function(pkg){
  new.pkg <- pkg[!(pkg %in% installed.packages()[, "Package"])]
  if (length(new.pkg)) 
    install.packages(new.pkg, dependencies = TRUE)
  sapply(pkg, require, character.only = TRUE)
}

#specify a list of required packages
pack_list <- c("dplyr",
               "lubridate",
               "NCmisc")

#install and load packages
suppressWarnings(ipak(pack_list))

#define current working directory
current_wd <- dirname(rstudioapi::getActiveDocumentContext()$path)
setwd(current_wd)

#cross-check unused packages
used_packages <- list.functions.in.file(rstudioapi::getSourceEditorContext()$path) %>%
  names() %>%
  unique()
pack_list <- paste0("package:",unlist(pack_list))
print("Unused packages:")
print(setdiff(pack_list,used_packages))
print("Missing packages:")
print(setdiff(used_packages,pack_list))

```{r}
if (!require(plyr)) install.packages('plyr')
if (!require(tidyverse)) install.packages('tidyverse')
if (!require(httr)) install.packages('httr')
if (!require(jsonlite)) install.packages('jsonlite')
if (!require(zoo)) install.packages('zoo')
if (!require(lubridate)) install.packages('lubridate')
if (!require(uuid)) install.packages('uuid')
if (!require(pbmcapply)) install.packages('pbmcapply')
if (!require(readxl)) install.packages('readxl')
if (!require(jsonlite)) install.packages('jsonlite')
if (!require(purrr)) install.packages('purrr')
if (!require(stringr)) install.packages('stringr')

library(plyr)
library(tidyverse)
library(httr)
library(jsonlite)
library(zoo)
library(lubridate)
library(uuid)
library(pbmcapply)
library(readxl)
library(jsonlite)
library(purrr)
library(stringr)
```

Get governor data

```{r}
objectIDs <- read.csv(file="events/objectIDs.csv",
                      header=TRUE,
                      sep=";")
measureIDs <- read.csv(file="events/measureIDs.csv",
                       header=TRUE,
                       sep=";") %>%
                .[which(.$source=="leader"),]
                
#get pm data, save as .csv file
governor <- read.csv(file="events/pms.csv",
                     header=TRUE,
                     sep=";",
                     dec=".")
save(governor,
     file="events/states_de_pms_data_csv.rda")

#extract required information per date, for sake of simplicity assuming same timezone/time for all dates
governor <- mutate(governor,
                   daysSinceBirth=dmy(daysSinceBirth),
                   daysSinceStart=dmy(daysSinceStart),
                   daysToEnd=dmy(daysToEnd),
                   .keep="unused") %>%
              left_join(.,
                        objectIDs,
                        by="description") %>%
              select(.,
                     -c(description,iso))

#ensure that there are records for each combination of iso and date (assuming that no dates are missing between min and max of original data)
governor <- expand.grid(unique(governor$uuidObject),
                        seq(max(governor$daysSinceStart),ymd("2020-12-31"),by="days")) %>%
              left_join(.,
                        governor,
                        by=c("Var1"="uuidObject")) %>%
              mutate(.,
                     uuidObject=Var1,
                     daysSinceBirth=as.integer(Var2-daysSinceBirth),
                     daysSinceStart=as.integer(Var2-daysSinceStart),
                     daysToEnd=as.integer(daysToEnd-Var2)) %>%
              mutate(.,
                     measurementTime=Var2,
                     percentTerm=daysSinceStart/(daysSinceStart+daysToEnd)) %>%
              select(.,
                     uuidObjectType,
                     uuidObject,
                     measurementTime,
                     party,
                     gender,
                     daysSinceBirth,
                     daysSinceStart,
                     daysToEnd,
                     percentTerm) %>%
              mutate(.,
                     party=case_when(party=="c" ~ 1,
                                     party=="spd" ~ 2,
                                     party=="green" ~ 3,
                                     party=="left" ~ 4,
                                     TRUE ~ 0),
                     gender=case_when(gender=="male" ~ 1,
                                      gender=="female" ~ 2,
                                      TRUE ~ 0))

#prepare event-based format
governor <- pivot_longer(governor,
                         cols=party:percentTerm,
                         names_to="measurement_description",
                         values_to="measurementValue",
                         values_transform=list(measurementValue=as.character)) %>%
                 na.omit(.,
                         measurementValue) %>%
                 left_join(.,
                           measureIDs,
                           by=c("measurement_description"="description")) %>%
                 mutate(.,
                        eventType=paste0(uuidObjectType,
                                         "_",
                                         uuidMeasure),
                        uuidObject=as.factor(uuidObject),
                        measurementValue=as.character(measurementValue)) %>%
                 select(.,
                        c(eventType,
                          uuidObject,
                          measurementTime,
                          measurementValue))

#function to save data by event type
save_group <- function(data,
                       eventType) {
  save(data,
       file=paste0("events/",
                   eventType,
                   ".rda"))
}
  
#save data  
governor %>%
  group_by(eventType) %>%
  group_walk(~ save_group(.x,
                          .y$eventType))
```
