---
title: "C3.ai cep daily change notebook"
output: html_notebook
---

# C3.ai COVID-19 Data Lake - Complex Event Processing for Daily Changes

This notebook uses time series from the abstraction layer to generate new time series (complex event processing approach). This specific notebook uses cumulated data to create daily changes.

For the time being, we are using a simplified model in which only the data segment but not the header segment will be created for event types.

To view an outline of this notebook, use the RStudio keyboard shortcut Control + Shift + O on Windows or Command + Shift + O on Mac.

Remark: Some of the packages may not be needed, use the following (sample) code to load packages instead:

#define a function to install and load required packages
ipak <- function(pkg){
  new.pkg <- pkg[!(pkg %in% installed.packages()[, "Package"])]
  if (length(new.pkg)) 
    install.packages(new.pkg, dependencies = TRUE)
  sapply(pkg, require, character.only = TRUE)
}

#specify a list of required packages
pack_list <- c("dplyr",
               "lubridate",
               "NCmisc")

#install and load packages
suppressWarnings(ipak(pack_list))

#define current working directory
current_wd <- dirname(rstudioapi::getActiveDocumentContext()$path)
setwd(current_wd)

#cross-check unused packages
used_packages <- list.functions.in.file(rstudioapi::getSourceEditorContext()$path) %>%
  names() %>%
  unique()
pack_list <- paste0("package:",unlist(pack_list))
print("Unused packages:")
print(setdiff(pack_list,used_packages))
print("Missing packages:")
print(setdiff(used_packages,pack_list))

```{r}
if (!require(plyr)) install.packages('plyr')
if (!require(dplyr)) install.packages('dplyr')
if (!require(pbmcapply)) install.packages('pbmcapply')
if (!require(stats)) install.packages('stats')
if (!require(lubridate)) install.packages('lubridate')
if (!require(data.table)) install.packages('data.table')

library(plyr)
library(dplyr)
library(pbmcapply)
library(stats)
library(lubridate)
library(data.table)
```

Define some basic parameters for data selection

```{r}
#define time threshold for preceding events
seconds_max_back <- 36*60*60
```

Get desired event types

```{r}
event_scope <- read.csv(file="cep/event_scope_cep_jhu_change.csv",
                        header=TRUE,
                        sep=";")
print(paste0(nrow(event_scope),
             " event types requested"))
event_scope$eventType <- paste0(event_scope$uuidObjectType,
                                "_",
                                event_scope$uuidMeasure)
event_scope$eventTypeNew <- paste0(event_scope$uuidObjectType,
                                   "_",
                                   event_scope$uuidMeasureNew)
event_scope <- select(event_scope,
                      eventType,
                      eventTypeNew)

files <- pbmclapply(1:nrow(event_scope),FUN=function(x) {
  list.files(path="events/",
             pattern=event_scope[x,]$eventType)
},mc.cores=8L) %>%
  unlist()
print(paste0(length(files),
             " event types found"))

event_records <- pbmclapply(files,FUN=function(x) {
  load(paste0("events/",
              x))
  data$measurementTime <- with_tz(data$measurementTime,
                                  tzone="UTC")
  return(data.frame(eventType=substr(x,
                                     1,
                                     nchar(x)-4),
                    data,
                    stringsAsFactors=FALSE))
},mc.cores=8L) %>%
  ldply(.parallel=TRUE)  %>%
  data.table(.) %>%
  setorder(.,
           eventType,
           uuidObject,
           -measurementTime) %>%
  distinct(.,
           .keep_all=TRUE)
print(paste0(nrow(event_records),
             " events loaded"))
```

Group records by event type and object, find most recent preceding value (within limits), calculate difference

```{r}
records <- event_records
records_previous <- records[,shift(.SD,
                                   n=-1,
                                   fill=NA,
                                   type="lag"),
                            by=c("eventType","uuidObject"),
                            .SDcols=3:4] %>%
                      .[,3:4]
records <- cbind(records,
                 records_previous)
colnames(records)[5:6] <- c("measurementTimeShifted",
                            "measurementValueShifted")
records$timeDiff <- difftime(records$measurementTime,
                             records$measurementTimeShifted,
                             tz="UTC",
                             units="secs")
records <- records[which(records$timeDiff>0 & records$timeDiff<=seconds_max_back),]

#prepare new events
records$measurementValue <- as.character(as.numeric(records$measurementValue) - as.numeric(records$measurementValueShifted))
records <- select(records,
                  eventType:measurementValue)
records <- left_join(records,
                     select(event_scope,
                            eventType,
                            eventTypeNew),
                     by="eventType") %>%
             mutate(.,
                    eventType=eventTypeNew) %>%
             select(.,
                    eventType,
                    uuidObject,
                    measurementTime,
                    measurementValue)

#function to save data by event type (should actually be made available as a basic function)
save_group <- function(data,
                       eventType) {
  save(data,
       file=paste0("events/",
                   eventType,
                   ".rda"))
  
}

records %>%
  group_by(eventType) %>%
  group_walk(~ save_group(.x,
                          .y$eventType))

print(paste0(length(unique(records$eventType)),
             " new event types created"))
print(paste0(length(unique(records$uuidObject)),
             " objects saved"))
```

