---
title: "C3.ai cep case/death ratio notebook"
output: html_notebook
---

# C3.ai COVID-19 Data Lake - Complex Event Processing for Case/Death Ratios

This notebook uses time series from the abstraction layer to generate new time series (complex event processing approach). This specific notebook divides JHU case/death data by population.

For the time being, we are using a simplified model in which only the data segment but not the header segment will be created for event types.

To view an outline of this notebook, use the RStudio keyboard shortcut Control + Shift + O on Windows or Command + Shift + O on Mac.

Remark: Some of the packages may not be needed, use the following (sample) code to load packages instead:

#define a function to install and load required packages
ipak <- function(pkg){
  new.pkg <- pkg[!(pkg %in% installed.packages()[, "Package"])]
  if (length(new.pkg)) 
    install.packages(new.pkg, dependencies = TRUE)
  sapply(pkg, require, character.only = TRUE)
}

#specify a list of required packages
pack_list <- c("dplyr",
               "lubridate",
               "NCmisc")

#install and load packages
suppressWarnings(ipak(pack_list))

#define current working directory
current_wd <- dirname(rstudioapi::getActiveDocumentContext()$path)
setwd(current_wd)

#cross-check unused packages
used_packages <- list.functions.in.file(rstudioapi::getSourceEditorContext()$path) %>%
  names() %>%
  unique()
pack_list <- paste0("package:",unlist(pack_list))
print("Unused packages:")
print(setdiff(pack_list,used_packages))
print("Missing packages:")
print(setdiff(used_packages,pack_list))

```{r}
if (!require(plyr)) install.packages('plyr')
if (!require(dplyr)) install.packages('dplyr')
if (!require(pbmcapply)) install.packages('pbmcapply')
if (!require(stats)) install.packages('stats')
if (!require(lubridate)) install.packages('lubridate')
if (!require(data.table)) install.packages('data.table')
if (!require(fuzzyjoin)) install.packages('fuzzyjoin')
if (!require(matrixStats)) install.packages('matrixStats')

library(plyr)
library(dplyr)
library(pbmcapply)
library(stats)
library(lubridate)
library(data.table)
library(matrixStats)
```

Define some basic parameters for data selection

```{r}
#define which events count as being recorded at the same time
seconds_backward <- 12*60*60-1
seconds_forward <- 12*60*60-1
```

Get desired event types

```{r}
event_scope <- read.csv(file="cep/event_scope_cep_jhu_ratio.csv",
                        header=TRUE,
                        sep=";")
print(paste0(nrow(event_scope)*2,
             " event types requested"))
event_scope$eventTypeDividend <- paste0(event_scope$uuidObjectTypeDividend,
                                        "_",
                                        event_scope$uuidMeasureDividend)
event_scope$eventTypeDivisor <- paste0(event_scope$uuidObjectTypeDividend,
                                       "_",
                                       event_scope$uuidMeasureDivisor)
event_scope$eventTypeNew <- paste0(event_scope$uuidObjectTypeDividend,
                                   "_",
                                   event_scope$uuidMeasureNew)
event_scope <- select(event_scope,
                      eventTypeDividend,
                      eventTypeDivisor,
                      eventTypeNew)
event_check <- c(event_scope$eventTypeDividend,
                 event_scope$eventTypeDivisor)

files <- pbmclapply(1:length(event_check),FUN=function(x) {
  list.files(path="events/",
             pattern=event_check[x])
},mc.cores=8L) %>%
  unlist()
print(paste0(length(files),
             " event types found"))

event_records <- pbmclapply(files,FUN=function(x) {
  load(paste0("events/",
              x))
  data$measurementTime <- with_tz(data$measurementTime,
                                  tzone="UTC")
  return(data.frame(eventType=substr(x,
                                     1,
                                     nchar(x)-4),
                    data,
                    stringsAsFactors=FALSE))
},mc.cores=8L) %>%
  ldply(.parallel=TRUE)  %>%
  data.table(.) %>%
  setorder(.,
           eventType,
           uuidObject,
           -measurementTime) %>%
  distinct(.,
           .keep_all=TRUE)
print(paste0(nrow(event_records),
             " events loaded"))

event_types_found <- unique(event_records$eventType)
print(paste0(length(event_types_found),
             " event types in data"))
```

Collect data in simultaneous chunks (simultaneous in terms of timestamps) - data recorded not more than seconds_backward ago and not more than seconds_forward in the future are considered to be recorded at the same time - and then create samples for pairs of events on that basis

```{r}
#reduce event scope to events that have been found
event_scope <- event_scope %>%
                 filter(.,
                        event_scope$eventTypeDividend %in% event_types_found) %>%
                 filter(.,
                        event_scope$eventTypeDivisor %in% event_types_found)

print("Processing events")
records <- event_records %>%
  group_by(eventType) %>%
  distinct(.,
           eventType,
           uuidObject,
           measurementTime,
           .keep_all=TRUE) %>%
  ungroup()

#function to save data by event type (should actually be made available as a basic function)
save_group <- function(data,
                       eventType) {
  save(data,
       file=paste0("events/",
                   eventType,
                   ".rda"))
  
}
  
pbmclapply(1:nrow(event_scope),FUN=function(x) {
  records_a <- records %>%
    filter(eventType==event_scope[x,]$eventTypeDividend) %>%
    mutate(.,
           validity=interval(measurementTime-seconds_backward,
                             measurementTime+seconds_forward))
  records_b <- records %>%
    filter(eventType==event_scope[x,]$eventTypeDivisor) %>%
    mutate(.,
           validity=interval(measurementTime-seconds_backward,
                             measurementTime+seconds_forward))
  records <- inner_join(records_a,
                        records_b,
                        by="uuidObject") %>%
               .[which(int_overlaps(.$validity.x,
                                    .$validity.y)),]
  
  #execution calculation
  records$measurementValue <- as.numeric(records$measurementValue.x) / as.numeric(records$measurementValue.y)
  records$measurementTime <- lubridate::intersect(records$validity.x,
                                                  records$validity.y)
  records$measurementTime <- records$measurementTime@start + records$measurementTime@.Data
  
  #clean results
  records <- select(records,
                    uuidObject,
                    measurementTime,
                    measurementValue,
                    eventType.x,
                    eventType.y) %>%
               left_join(.,
                         event_scope,
                         by=c("eventType.x"="eventTypeDividend",
                              "eventType.y"="eventTypeDivisor")) %>%
               select(.,
                      -c(eventType.x,
                         eventType.y)) %>%
               .[order(.$measurementTime,
                       decreasing=TRUE),] %>%
               distinct(.,
                        uuidObject,
                        measurementTime,
                        .keep_all=TRUE) %>%
               .[which(!is.infinite(.$measurementValue)),] %>%
               mutate(.,
                      measurementValue=as.character(measurementValue))
  
  records %>%
    group_by(eventTypeNew) %>%
    group_walk(~ save_group(.x,
                            .y$eventTypeNew))
  
  print(paste0(length(unique(records$eventTypeNew)),
               " new event types created"))
  print(paste0(length(unique(records$uuidObject)),
               " objects saved"))
},mc.cores=8L)
```
