---
title: "C3.ai cep notebook"
output: html_notebook
---

# C3.ai COVID-19 Data Lake - Complex Event Processing

This notebook uses time series from the abstraction layer to generate new time series (complex event processing approach). This specific notebook calculates daily from cumulated data.

To view an outline of this notebook, use the RStudio keyboard shortcut Control + Shift + O on Windows or Command + Shift + O on Mac. 

```{r}
if (!require(plyr)) install.packages('plyr')
if (!require(dplyr)) install.packages('dplyr')
if (!require(pbmcapply)) install.packages('pbmcapply')
if (!require(stats)) install.packages('stats')
if (!require(lubridate)) install.packages('lubridate')
if (!require(data.table)) install.packages('data.table')
if (!require(tidyr)) install.packages('tidyr')

library(plyr)
library(dplyr)
library(pbmcapply)
library(stats)
library(lubridate)
library(data.table)
library(tidyr)
```

The following code is taken from: https://github.com/Stochastik-TU-Ilmenau/COVID-19/blob/gh-pages/estimator.r
See also: https://stochastik-tu-ilmenau.github.io/COVID-19/

```{r}
# infectivity profile:
infectivity <- c((0:3)/3, 1, (5:0)/5)
names(infectivity) <- seq_along(infectivity)
infectivity <- infectivity / sum(infectivity)

width <- 1
report.delay <- 7
alpha <- 0.05

repronum <- function(
    new.cases, # I
    profile, # w
    window = 1, # H
    delay = 0, # Delta
    conf.level = 0.95, # 1-alpha
    pad.zeros = FALSE,
    min.denominator = 5,
    min.numerator = 5
) {
    # pad zeros if desired
    if(pad.zeros) new.cases <- c(rep(0, length(profile) - 1), new.cases)

    # compute convolutions over h, tau and both, respectively
    sum.h.I <- as.numeric(stats::filter(new.cases, rep(1, window),
        method = "convolution", sides = 1))
    sum.tau.wI <- as.numeric(stats::filter(new.cases, c(0, profile),
        method = "convolution", sides = 1))
    sum.htau.wI <- as.numeric(stats::filter(sum.tau.wI, rep(1, window),
        method = "convolution", sides = 1))

    # estimators
    repronum <- ifelse(sum.h.I < min.numerator, NA, sum.h.I) / ifelse(sum.htau.wI < min.denominator, NA, sum.htau.wI)

    # standard errors
    repronum.se <- sqrt(repronum / sum.htau.wI)

    # shift by delay
    repronum <- c(repronum, rep(NA, delay))[(1:length(repronum)) + delay]
    repronum.se <- c(repronum.se,
        rep(NA, delay))[(1:length(repronum.se)) + delay]

    # standard normal quantile
    q <- qnorm(1 - (1-conf.level) / 2)

    # return data.frame with as many rows as new.cases
    ret <- data.frame(
        repronum = repronum,
        repronum.se = repronum.se,
        ci.lower = repronum - q * repronum.se,
        ci.upper = repronum + q * repronum.se
    )
    if(pad.zeros) ret[-(1:(length(profile)-1)),] else ret
}
```

Get desired event types

```{r}
event_scope <- read.csv(file="cep/event_scope_cep_r.csv",
                        header=TRUE,
                        sep=";")
print(paste0(nrow(event_scope),
             " event types requested"))
event_scope$eventType <- paste0(event_scope$uuidObjectType,
                                "_",
                                event_scope$uuidMeasure)

files <- pbmclapply(1:nrow(event_scope),FUN=function(x) {
  list.files(path="events/",
             pattern=event_scope[x,]$eventType)
},mc.cores=8L) %>%
  unlist()
print(paste0(length(files),
             " event types found"))

event_records <- pbmclapply(files,FUN=function(x) {
  load(paste0("events/",
              x))
  data$measurementTime <- with_tz(data$measurementTime,
                                  tzone="UTC")
  return(data.frame(eventType=substr(x,
                                     1,
                                     nchar(x)-4),
                    data,
                    stringsAsFactors=FALSE))
},mc.cores=8L) %>%
  ldply(.parallel=TRUE)  %>%
  data.table(.) %>%
  setorder(.,
           eventType,
           uuidObject,
           -measurementTime) %>%
  distinct(.,
           .keep_all=TRUE) %>%
  left_join(.,
            event_scope,
            by="eventType") %>%
  select(.,
         c(eventType,
           uuidObjectType,
           uuidObject,
           measurementTime,
           measurementValue))
print(paste0(nrow(event_records),
             " events loaded"))
```

Group records by event type and object, find most recent preceding value (within limits), calculate difference

```{r}
r_values <- event_records %>%
              group_by(eventType,
                       uuidObject) %>%
              group_modify(~ repronum(.x$measurementValue,
                                      infectivity)) %>%
              ungroup() %>%
              select(.,
                     -c(eventType,
                        uuidObject))
new_measure_names <- event_scope %>%
                       select(.,-c(uuidObjectType,uuidMeasure,eventType)) %>%
                       distinct(.)
colnames(r_values) <- new_measure_names
event_records <- event_records %>%
                   select(.,
                          -measurementValue) %>%
                   cbind(.,
                         r_values)

#prepare new events
event_records <- pivot_longer(event_records,
                              cols=5:8,
                              names_to="measurement_description",
                              values_to="measurementValue",
                              values_transform=list(measurementValue=as.character)) %>%
                 na.omit(.,
                         measurementValue) %>%
                 mutate(.,
                        eventType=paste0(uuidObjectType,
                                         "_",
                                         measurement_description),
                        uuidObject=as.factor(uuidObject),
                        measurementValue=as.character(measurementValue)) %>%
                 select(.,
                        c(eventType,
                          uuidObject,
                          measurementTime,
                          measurementValue))

#function to save data by event type (should actually be made available as a basic function)
save_group <- function(data,
                       eventType) {
  save(data,
       file=paste0("events/",
                   eventType,
                   ".rda"))
  
}

event_records %>%
  group_by(eventType) %>%
  group_walk(~ save_group(.x,
                          .y$eventType))

print(paste0(length(unique(event_records$eventType)),
             " new event types created"))
print(paste0(length(unique(event_records$uuidObject)),
             " objects saved"))
```

